SpikeIn MSstatsPTM Analysis

### 2022-07-08 code/Spike-in_Analysis.Rmd
updated spikein sections, methods, and results

summary_df$PTM$RunlevelData

@@

## Update some naming conventions
plot_df[plot_df$Label == 'mix1-mix3'][['contrast_truth']] <- "LogFC: 1 (mix1-mix3)"
plot_df[plot_df$Label == 'mix1-mix4'][['contrast_truth']] <- "LogFC: 0 (mix1-mix4)"
plot_df[plot_df$Label == 'mix2-mix3'][['contrast_truth']] <- "LogFC: -2 (mix2-mix3)"
plot_df[plot_df$Label == 'mix2-mix4'][['contrast_truth']] <- "LogFC: -1 (mix2-mix4)"

plot_df[plot_df$labeling == 'light'][['labeling']] <- "Background Peptides"
plot_df[plot_df$labeling == 'heavy'][['labeling']] <- "SpikeIn Peptides"

@@

# Volcano plot
png("../supplementary/sim_new/spike_in_msstatsptm_volcano.png", width = 750, height = 500)
plot_df %>% arrange(labeling) %>% 
  filter(abs(log2FC) < Inf & Label %in% c("mix1-mix3", "mix1-mix4", "mix2-mix3", "mix2-mix4")) %>%
  ggplot(aes(log2FC, -log10(adj.pvalue))) + 
  geom_point(aes(color = labeling, alpha = labeling), size = 2.2) + 
  scale_color_manual(values = c("#999999", "#D55E00")) + 
  scale_alpha_manual(values = c(0.2, 1)) + 
  #scale_size_manual(values = c(2, 1)) + 
  geom_hline(yintercept = 0) + 
  geom_vline(xintercept = 0, linetype = "dashed") + 
  geom_hline(yintercept = -log10(0.05), color = "darkred") + 
  facet_grid(protadj ~ contrast_truth) + 
  theme_bw() + 
  theme(axis.text.x = element_text(size = 16), 
       axis.text.y = element_text(size = 16), 
       legend.text=element_text(size=16),
       axis.title.y = element_text(size = 18, vjust=2),
       axis.title.x = element_text(size = 18),
       title = element_text(size = 20),
       strip.text = element_text(size = 15),
       legend.title =  element_blank(),
       legend.position = "bottom",
       legend.box.margin=margin(-10,-10,-10,-10)) + 
  scale_y_continuous(limits = c(0,5)) + 
  guides(colour = guide_legend(override.aes = list(size=5))) +
  labs(title = "Proposed Method VolcanoPlot")
dev.off()
```

@@

# Volcano plot
png("../supplementary/sim_new/spike_in_limma_volcano.png", width = 750, height = 500)
plot_df %>% arrange(labeling) %>% 
  filter(abs(Log2FC) < Inf & Label %in% c("mix1-mix3", "mix1-mix4", "mix2-mix3", "mix2-mix4")) %>%
  ggplot(aes(Log2FC, -log10(adj.pvalue))) + 
  geom_point(aes(color = labeling, alpha = labeling), size = 2.2) + 
  scale_color_manual(values = c("#999999", "#D55E00")) + 
  scale_alpha_manual(values = c(0.2, 1)) + 
  #scale_size_manual(values = c(2, 1)) + 
  geom_hline(yintercept = 0) + 
  geom_vline(xintercept = 0, linetype = "dashed") + 
  geom_hline(yintercept = -log10(0.05), color = "darkred") + 
  facet_grid(protadj ~ contrast_truth) + 
  theme_bw() + 
  theme(axis.text.x = element_text(size = 16), 
       axis.text.y = element_text(size = 16), 
       legend.text=element_text(size=16),
       axis.title.y = element_text(size = 18, vjust=2),
       axis.title.x = element_text(size = 18),
       title = element_text(size = 20),
       strip.text = element_text(size = 15),
       legend.title =  element_blank(),
       legend.position = "bottom",
       legend.box.margin=margin(-10,-10,-10,-10)) + 
  scale_y_continuous(limits = c(0,3)) + 
  guides(colour = guide_legend(override.aes = list(size=5))) +
  labs(title = "Limma VolcanoPlot")
dev.off()
```

>>>>

@@

## Update some naming conventions
plot_df[plot_df$Label == 'mix2 vs mix1'][['contrast_truth']] <- "LogFC: -1 (mix2-mix1)"
plot_df[plot_df$Label == 'mix3 vs mix1'][['contrast_truth']] <- "LogFC: 1 (mix3-mix1)"
plot_df[plot_df$Label == 'mix4 vs mix1'][['contrast_truth']] <- "LogFC: 0 (mix4-mix1)"
plot_df[plot_df$Label == 'mix3 vs mix2'][['contrast_truth']] <- "LogFC: 2 (mix3-mix2)"
plot_df[plot_df$Label == 'mix4 vs mix2'][['contrast_truth']] <- "LogFC: 1 (mix4-mix2)"
plot_df[plot_df$Label == 'mix4 vs mix3'][['contrast_truth']] <- "LogFC: -1 (mix4-mix3)"
plot_df$contrast_truth = factor(plot_df$contrast_truth, levels = 
                                  c("LogFC: -1 (mix2-mix1)",
                                    "LogFC: 1 (mix3-mix1)",
                                    "LogFC: 0 (mix4-mix1)",
                                    "LogFC: 2 (mix3-mix2)",
                                    "LogFC: 1 (mix4-mix2)",
                                    "LogFC: -1 (mix4-mix3)"))

plot_df[plot_df$labeling == 'light'][['labeling']] <- "Background Peptides"
plot_df[plot_df$labeling == 'heavy'][['labeling']] <- "Spike-in Peptides"

@@

# Volcano plot
png("../supplementary/sim_new/spike_in_msstatsptm_volcano.png", width = 1000, height = 500)
plot_df %>% arrange(labeling) %>% 
  filter(abs(log2FC) < Inf) %>% # & Label %in% c("mix1-mix3", "mix1-mix4", "mix2-mix3", "mix2-mix4")
  ggplot(aes(log2FC, -log10(adj.pvalue))) + 
  geom_point(aes(color = labeling, alpha = labeling), size = 2.2) + 
  scale_color_manual(values = c("#999999", "#D55E00")) + 
  scale_alpha_manual(values = c(0.2, 1)) + 
  #scale_size_manual(values = c(2, 1)) + 
  geom_hline(yintercept = 0) + 
  geom_vline(xintercept = 0) + 
  geom_vline(aes(xintercept = trueLog2FC),color = "darkred", linetype= "dashed") +
  geom_hline(yintercept = -log10(0.05), color = "darkred") + 
  facet_grid(protadj ~ contrast_truth) + 
  theme_bw() + 
  theme(axis.text.x = element_text(size = 16), 
       axis.text.y = element_text(size = 16), 
       legend.text=element_text(size=16),
       axis.title.y = element_text(size = 18, vjust=2),
       axis.title.x = element_text(size = 18),
       title = element_text(size = 20),
       strip.text = element_text(size = 15),
       legend.title =  element_blank(),
       legend.position = "bottom",
       legend.box.margin=margin(-10,-10,-10,-10)) + 
  scale_y_continuous(limits = c(0,5)) + 
  guides(colour = guide_legend(override.aes = list(size=5))) +
  labs(title = "Proposed Method VolcanoPlot")
dev.off()
```

@@

# Volcano plot
png("../supplementary/sim_new/spike_in_limma_volcano.png", width = 750, height = 500)
plot_df %>% arrange(labeling) %>% 
  filter(abs(Log2FC) < Inf & Label %in% c("mix1-mix3", "mix1-mix4", "mix2-mix3", "mix2-mix4")) %>%
  ggplot(aes(Log2FC, -log10(adj.pvalue))) + 
  geom_point(aes(color = labeling, alpha = labeling), size = 2.2) + 
  scale_color_manual(values = c("#999999", "#D55E00")) + 
  scale_alpha_manual(values = c(0.2, 1)) + 
  #scale_size_manual(values = c(2, 1)) + 
  geom_hline(yintercept = 0) + 
  geom_vline(xintercept = 0) + 
  geom_vline(aes(xintercept = trueLog2FC),color = "darkred", linetype= "dashed") +
  geom_hline(yintercept = -log10(0.05), color = "darkred") + 
  facet_grid(protadj ~ contrast_truth) + 
  theme_bw() + 
  theme(axis.text.x = element_text(size = 16), 
       axis.text.y = element_text(size = 16), 
       legend.text=element_text(size=16),
       axis.title.y = element_text(size = 18, vjust=2),
       axis.title.x = element_text(size = 18),
       title = element_text(size = 20),
       strip.text = element_text(size = 15),
       legend.title =  element_blank(),
       legend.position = "bottom",
       legend.box.margin=margin(-10,-10,-10,-10)) + 
  scale_y_continuous(limits = c(0,3)) + 
  guides(colour = guide_legend(override.aes = list(size=5))) +
  labs(title = "Limma VolcanoPlot")
dev.off()
```
